\documentclass[runningheads]{llncs}

\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}

\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO}: {#1}}}

\begin{document}

% Please feel free to suggest a better title
\title{An Assurance Pattern for Cyber-Resilient Systems Engineering}

\author{
	Isaac Amundson\inst{1} 
	\and Darren Cofer\inst{1} 
	\and David Hardin\inst{1} 
	\and John Hatcliff\inst{2}}

\institute{
	Applied Research and Technology, Collins Aerospace, USA \\
	\email{\{isaac.amundson,darren.cofer,david.hardin\}@collins.com}\\
	\and Kansas State University, USA \\
	\email{hatcliff@ksu.edu}
}

\authorrunning{I. Amundson et al.}

\maketitle

\begin{abstract}

On the DARPA Cyber Assured Systems Engineering (CASE) program, our team has developed BriefCASE, an open-source model-based engineering environment for cyber-resilient system design.  BriefCASE is comprised of tools that emit evidence of correctness that is maintained by the framework and can be used to substantiate assurance claims.  
In this paper, we describe a comprehensive cyber-resiliency assurance pattern, which BriefCASE instantiates with the system under development. Evidence collected by the framework is automatically evaluated in the resulting assurance case to determine whether cyber-resiliency goals have been acceptably satisfied.

\end{abstract}

DISTRIBUTION STATEMENT A. Approved for public release: distribution unlimited.

% Include short CASE / BriefCASE overview
\section{Introduction}
\label{sec:introduction}
\input{introduction}


% Section 1: CASE description 
% Be specific about differences with D-MILS
% Section 2: Description of Briefcase workflow
% Section 3: Walk through assurance pattern


% Include DMILS - compare/contrast
% Integrate this section with Intro if short on space
%\section{Related Work}
%\label{sec:related-work}
%\input{related-work}

\section{Cyber Assured Systems Engineering with BriefCASE}
\label{sec:briefcase}
\input{briefcase}

% Start high-level, go as low-level as space allows
% Don't go into too much detail of model argument, instead refer to Destion paper
% Spend more time on implementation argument?
\section{BriefCASE Cyber-Resiliency Assurance Pattern}
\label{sec:assurance-pattern}
\input{assurance-pattern}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

\section{Acknowledgment}
This work was funded by DARPA contract HR00111890001. The views, opinions and/or findings expressed are those of the authors and should not be interpreted as representing the official views or policies of the Department of Defense or the U.S. Government.

\bibliographystyle{splncs04}
\bibliography{biblio}

\end{document}
